### 2020-07-22 eda.Rmd
Remake Table VII

library(tidyverse)
library(haven)

@@

```{r}

combined <- combined  %>%
  # turn dollars into hundreds of dollars
  mutate(
    totbal = totbal / 100,
    newtotbal = newtotbal / 100
  ) %>%
  # fix population variable
  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
  # create bank penetration variable%>%
  mutate(brgy_penetration = no_clients / pop)

combined <- combined %>%
  group_by(brgy_penetration) %>%
  mutate(sd_totbal = sd(totbal),
         mean_totbal = mean(totbal)) %>%
  ungroup()

treated <- combined %>%
  filter(!is.na(treatment))

@@

Questions:

@@

Our questions:

* Remake table 2 with non-parametric standard errors
* Remake table 3 (meh)
* Remake table 6
* Remake table 7

* Did the respondents make positive savings?
* What proportion of people opened the account?
* Did the treatment group save more than the control group?
* estimate the pdf of savings and then estimate the percentiles

```{r}
count(combined, group)

>>>>

library(tidyverse)
library(haven)
library(quantreg)
```

@@

```{r}
combined <- combined  %>%
  # turn dollars into hundreds of dollars
  mutate(
    totbal = totbal / 100,
    newtotbal = newtotbal / 100
  ) %>%
  # fix population variable
  mutate(pop = as.numeric(str_replace(pop, ",", ""))) %>%
  # create bank penetration variable%>%
  mutate(brgy_penetration = no_clients / pop)

combined <- combined %>%
  # calculate the mean and sd for each bank
  # the Stata code is a little cyptic
  group_by(brgy_penetration) %>%
  mutate(sd_totbal = sd(totbal),
         mean_totbal = mean(totbal)) %>%
  ungroup()

# create a set with the 1777 observations that are in the SEED, 
# marketing treatment, or control group
treated <- combined %>%
  filter(!is.na(treatment))

@@

## Remake Table VII

```{r}
rq(as.numeric(balchange) ~ treatment + marketing, 
   tau = seq(from = 0.1, to = 0.9, by = 0.1),
   data = filter(seed011204, !is.na(treatment)))

rq(as.numeric(balchange) ~ treatment + marketing, 
   tau = seq(from = 0.1, to = 0.9, by = 0.1),
   data = treated)
```

## Questions

* Remake table 6 with bootstrapped standard errors
* Remake table 7 with kernel density estimators and compare with the percentiles percentiles from the quantile regression
* Estimate the proportion of people who would open an account
* Do a k-sample test to compare the savings or change in svaings of the three groups. Then do pair-wise tests with corrections for multiple testing. 
* We can use LOESS/KDE to compare any of the bivariate relationships
    * Year of education by totbal or change in totbal
    * Age or age2 by totbal or change in totbal

@@
